Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-05-02 paper/paper.tex
Fixed a typo

\citeauthor{van2012systematic} proposed the Abstracting Abstract Machines (AAM) methodology which provides a recipe
for constructing sound abstract interpreters for higher-order functional languages from concrete abstract machines
~\cite{van2012systematic, van2010abstracting}.
Given a concrete small-step abstract machine, (e.g, the CESK machine, Krivine's machine, etc.),
by allocating continuations in the store and bounding both the value addresses and continuation
addresses to be finite, we obtain an abstract interpreter with a finite state space which
can be used for performing sound static analysis.
One can further instantiate different polyvariant control flow analyses by using different address allocators \cite{Gilray:2016:ACP:2951913.2951936}.

>>>>

\citeauthor{van2012systematic} proposed the Abstracting Abstract Machines (AAM) methodology which provides a recipe
for constructing sound abstract interpreters for higher-order functional languages from concrete abstract machines
~\cite{van2012systematic, van2010abstracting}.
Given a concrete small-step abstract machine (e.g. the CESK machine, Krivine's machine, etc.),
by allocating continuations in the store and bounding both the value addresses and continuation
addresses to be finite, we obtain an abstract interpreter with a finite state space which
can be used for performing sound static analysis.
One can further instantiate different polyvariant control flow analyses by using different address allocators \cite{Gilray:2016:ACP:2951913.2951936}.
